---
title: "ASSIGN_3"
author: "Pjeanjud"
date: "2026-10-09"
output: html_document
---

```{r}
UniversalBank <- read.csv("UniversalBank.csv")


set.seed(123)

trainIndex <- sample(
  1:nrow(UniversalBank),
  0.60 * nrow(UniversalBank)
)

training <- UniversalBank[trainIndex, ]
validation <- UniversalBank[-trainIndex, ]

nrow(training)
nrow(validation)

names(UniversalBank)
```

a
```{r}
pivot_table <- table(training$CreditCard,
                     training$Online,
                     training$Personal.Loan)

pivot_table
```

b
```{r}
sum(training$CreditCard == 1 &
      training$Online == 1 &
      training$Personal.Loan == 1) /
  sum(training$CreditCard == 1 &
        training$Online == 1)
```

c
```{r}
table(training$Online, training$Personal.Loan)
table(training$CreditCard, training$Personal.Loan)
```

d
```{r}
#i.
mean(training$CreditCard[training$Personal.Loan == 1] == 1)

#ii.
mean(training$Online[training$Personal.Loan == 1] == 1)

#iii.
mean(training$Personal.Loan == 1)

#iv.
mean(training$CreditCard[training$Personal.Loan == 0] == 1)

#v.
mean(training$Online[training$Personal.Loan == 0] == 1)

#vi.
mean(training$Personal.Loan == 0)
```

e
```{r}
p1 <- (0.3273381 * 0.6438849 * 0.09266667)
p0 <- (0.2909625 * 0.5951506 * 0.9073333)
p1 / (p1 + p0)
```

f
I WOULD SAY THAT PART B(0.1071429) GIVES THE MOST CORRECT ANSWER BECAUSE THE PIVOT TABLE USE BOTH CREDIT CARD AND ONLINE BANKING TOGETHER TO GIVE THE ESTIMATE, WHEREAS NAIVE BAYES(0.1105637) GIVES A HIGHER ESTIMATE BECAUSE IT ASSUMES THAT  CREDIT CARD AND ONLINE BANKING ARE EACH INDEPENDENT.

g


```{r}
library(e1071)

training$CreditCard <- factor(training$CreditCard)
training$Online <- factor(training$Online)
training$Personal.Loan <- factor(training$Personal.Loan)

nb_model <- naiveBayes(
  Personal.Loan ~ CreditCard + Online,
  data = training

)


predict(nb_model,
        newdata = data.frame(
          CreditCard = factor(1, levels = c(0, 1)),
          Online = factor(1, levels = c(0, 1))
        ),
        type = "raw")
```
THE NAIVE BAYES GIVE A PROBABILITY OF 0.1105637 THAT A CUSTOMER WITH A CREDIT CARD WHO USES ONLINE BANKING WILL ACCEPT THE LOAN. SAME AS PART e
